Using Fundamental Measure Theory to treat the two-point pair distribution function of the Inhomogeneous Hard-Sphere Fluid

### 2013-06-25 papers/pair-correlation/paper.tex
added system to dadz.py so that if file is not there it does not exit just gives warning in the plot Tested everything on node39.

\section{What has been done before?}
\subsection{Gloor simple method, problematic}
\subsection{Fischer accurate but slow}

@@

\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
Figure~\ref{fig:radial-distribution} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/ghs-g}
  \includegraphics[width=3cm]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\subsection{Pair distribution function}
Figure~\ref{fig:pair-distribution} shows...
\begin{figure}
  \includegraphics[width=6cm]{figs/pair-correlation-2-395-5}
  \caption{Plot of the pair distribution function near a hard wall.
    How do we plot this?}\label{fig:pair-distribution}
\end{figure}

\section{How well does it work?}
Figure~\ref{fig:dadz} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/dadz-3-2}
  \includegraphics[width=3cm]{figs/dadz-3-3}
  %%\includegraphics[width=3cm]{figs/dadz-4-3}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall. For what $\Phi$?}\label{fig:dadz}
\end{figure}

@@

Plischke and Henderson worked out the pair correlation function near a
hard wall using Percus-Yevick, and compare with Monte Carlo
results\cite{plischke1986pair}.  They plot the pair correlation
function along interesting paths.

@@

Gloor et al \cite{gloor2007prediction} uses average density of two points and the uses
bulk radial distribution for the reference system (hard spheres) at
this density, in order to approximate pair correlation.

Gross \cite{gross2009density} does the same as Gloor et al except that
he uses a hard chain reference fluid.

>>>>

\section{What has been done before?}
\subsection{Gloor simple method, problematic}
Gil-Villegas\cite{gil1997statistical} approximates the first order inverse tenpurature Helmholtz Free energy term, which involves an integral of a potential multiplied by a radial distribution function $g^{HS}(r,\eta)$, by first taking the distribution function out of the integral and evaluating it at the correct mean distance $\zeta$, according to the mean value theorem.  They then approximate the pair correlation function $g^{HS}(\zeta,\eta)$ with the correlation at contact and at a effective $\eta_{eff}$.  The $\eta_{eff}$ is found by fitting a general function form to correct energy solutions $a_1$ with depenedent variable $\eta$ and

\subsection{Fischer accurate but slow}

@@

\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
Figure~\ref{fig:radial-distribution} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/ghs-g}
  \includegraphics[width=3cm]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\subsection{Pair distribution function}
Figure~\ref{fig:pair-distribution} shows...
\begin{figure}
  %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-0.pdf}
  \includegraphics[width=6cm]{figs/pair-correlation-2-395-5.pdf}
  %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-10.pdf}
  \caption{Plot of the pair distribution function near a hard wall.
    In the interest of space and memeory, we should look at the function and decided which data to add?}\label{fig:pair-distribution}
\end{figure}

\section{How well does it work?}
Figure~\ref{fig:dadz} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/dadz-3-2.pdf}
  \includegraphics[width=3cm]{figs/dadz-3-3.pdf}
  \includegraphics[width=3cm]{figs/dadz-2-2.pdf}
  \includegraphics[width=3cm]{figs/dadz-2-3.pdf}
  %%\includegraphics[width=3cm]{figs/dadz-4-3}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall. For what $\Phi$?}\label{fig:dadz}
\end{figure}

@@

Plischke and Henderson worked out the pair correlation function near a
hard wall using Percus-Yevick, and compare with Monte Carlo
results\cite{plischke1986pair}.  They plot the pair correlation
function along interesting paths.  \fixme{Jeff read this paper for a
  while and does not understand what they do in oder to find the pair
  correlation function as compared to the radial distribution function}

@@

Gloor et al \cite{gloor2007prediction} uses average density of two points:
\begin{align}
\overline{\rho} &\equiv \frac{\rho(\rr)+\rho(\rr')}{2}
\end{align}
and the uses bulk radial distribution for the reference system (hard
spheres) at this density, in order to approximate pair correlation.

Evans \cite{evans1992density}perscribes to use the same approximation but with an unspecified 'mean denisty':

\begin{align}
g^{(2)}(\rr_1,\rr_2) &\equiv g_r(\rho^m,\rr_{12})
\end{align}

Gross \cite{gross2009density} uses a hard chain reference fluid.  In
his functional he needs a pair correlation beween the different
segments of chains.  He approximates this function with the radial
distribution given by the Carnahan Starling at a density that is the
average density of the segment positions $\rr$ and $\rr'$:

\begin{align}
\overline{\rho} &\equiv \frac{\rho(\rr)+\rho(\rr')}{2}
\end{align}
